---
title: "Homework 5"
author: "Zhenyu Zhou"
date: "11/15/2022"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```



```{r load_libraries}
library(tidyverse)
```


## Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

## Problem 2

Describe the raw data.

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Test Baltimore, MD and get data.

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)
  ) %>% 
  broom::tidy()
```

Test each of the cities in dataset and get data.

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

Create a plot.

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(title = "Estimates of Proportions of Homicides in Each City") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 3 

Generate the datasets for mu = 0,1,2,3,4,5,6

```{r, files = T}
stimulation = function(mu, sd = 5, size = 30, iterate = 5000){
  stimulation = tibble(
    mu = mu,
    trial = seq(1:iterate),
    results = rerun(iterate, rnorm(size, mu, sd)))
  stimulation_df = stimulation %>%
    mutate(ttest = map(.x = results, ~t.test(.x))) %>% 
    mutate(pvalue = map(.x = ttest, ~broom::tidy(.x))) %>% 
    unnest(pvalue) %>% 
    select(mu, trial, estimate, p.value) %>%
    mutate(sample_mean = estimate, p_value = p.value, .keep = "unused",
           decision = case_when(
             p_value < 0.05 ~ "Reject",
             p_value >= 0.05 ~ "Fail to reject"
           ))
  return(stimulation_df)
}

stimulation_combine = tibble(
  output = map(.x = 0:6, ~stimulation(.x)))

stimulation_df = stimulation_combine %>% 
  unnest(cols = c(output))
```

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis

```{r The association between size effect and power, message = F}
stimulation_df %>% 
  group_by(mu) %>% 
  summarize(percent = length(decision[decision == "Reject"])/n()) %>% 
  as_tibble() %>% 
  ggplot(aes(x = mu, y = percent)) +
  geom_point(size = 1.5) +
  geom_line() +
  labs(
    title = "The association between effect size and power",
    x = "True value of μ",
    y = "Power") 
```

Describe the association between effect size and power.

It seems that power is positively associated with effect size that the power would increase as the true value of mu increased from 0 to 6 which means the effect size = (true mean - mu null) would increase. Since variance maintained the same and parameter mu null set to 0, it became more unlikely to see extreme cases of average estimate equals to 0 as the power increased. In other words, the rejection region would be larger as the distribution move leftwards.

Make a plot showing the average estimate of μ^ on the y axis and the true value of μ on the x axis; Make a second plot (or overlay on the first) the average estimate of μ^ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis


```{r, message = F}
all_df = stimulation_df %>% 
  group_by(mu) %>% 
  summarise(avgest_all = mean(sample_mean)) %>% 
  as_tibble()
rejected_df = stimulation_df %>% 
  filter(decision == "Reject") %>% 
  group_by(mu) %>% 
  summarise(avgest_rejected = mean(sample_mean)) %>% 
  as_tibble()
combine_df = left_join(all_df, rejected_df, by = "mu") %>% 
  pivot_longer(avgest_all:avgest_rejected,
               names_to = "type",
               names_prefix = "avgest_",
               values_to = "average_estimate")
```

```{r Average estimate of μ^ and the true value of μ}
combine_df %>% 
  filter(type == "all") %>% 
  ggplot(aes(x = mu, y = average_estimate)) +
  geom_point() +
  geom_line() +
  labs(
    title = "Average estimate of μ^ and the true value of μ",
    x = "True value of μ",
    y = "Average estimate")
```

```{r True value of μ and the average estimated μ^ in All and rejected samples}
combine_df %>% 
  ggplot(aes(x = mu, y = average_estimate, color = type)) +
  geom_point() +
  geom_line() +
  labs(
    title = "True value of μ and the average estimated μ^ in All and rejected samples",
    x = "True value of Mean",
    y = "Average estimate")
```

The sample average μ^ for all data is approximately equals to the true value of μ which consistent with the underlying population distribution.  

The sample average of μ^ across tests for which the null is rejected is approximately equal to the true value of μ unless the power of the test is not great enough.

When true value of μ is 0, the average of μ^ is approximately the same as the true value of μ because about same amounts of extreme cases are being rejected. When true value of μ equals to 1 or 2, only samples with greater sample means are rejected so that the average estimate of μ^ is larger than the true value of μ.

It is noticeable that the difference between the sample average of μ^ of rejected groups and the true values became smaller as the effect size increases. As more and more samples being rejected, the average estimate of μ^ is approximately equal to the true value.  
